### 2012-01-20 contents.tex
Writing background.

@@

Bug tracking systems allow users and developers of a software system to manage a list of bugs for the system. Usually, users and developers can report bugs, along with information such as steps to reproduce the bug, its severity, the operating system used etc. Developers choose bugs to fix and can report on the progress of the bug fixing activities, ask for clarification etc.

One important feature of a bug that is recorded on bug tracking systems is its status. The status records the progress of the bug fixing activity, and, as such, provides data to software engineering studies. Figure \ref{fig:bugzilla} shows each status that can be recorded in Bugzilla, a popular bug tracking system, along with typical transitions between status values, i.e., the workflow. Other systems present comparable status values and transitions.

@@

In the simplest cases, a bug is created and receive the status \texttt{UNCONFIRMED} (if it was created by a regular user) or \texttt{NEW} (if it was created by a developer). Next, it is assigned to a developer, and then it is resolved, possibly by fixing it with a patch on the source code. The solution is then verified by someone in the quality assurance team. If it passes the quality requirements, it is closed and the patch is added to the next release. If it doesn’t pass the quality requirements or if the solution only partially fixes the problem, the bug is reopened.

>>>>

% http://wiki.eclipse.org/Development_Resources/HOWTO/Bugzilla_Use
%   The severity tags aren't used much, except to distinguish enhancements from bugs. Typically the users specify severities as they see fit.

@@

Bug tracking systems allow users and developers of a software system to manage a list of bugs for the system. Usually, users and developers can report bugs, along with information such as steps to reproduce the bug, its severity and the operating system used. Developers choose bugs to fix and can report on the progress of the bug fixing activities, ask for clarification, discuss causes for the bug etc.

In this research, we focus on Bugzilla, an open source bug tracking system used by notable software projects such as Eclipse, Mozilla, Linux Kernel, Open Office, Apache, and companies such as NASA and Facebook\footnote{Complete list available at http://www.bugzilla.org/installation-list/.}. However, the general concepts from Bugzilla should apply to most other bug tracking systems.

One important feature of a bug that is recorded on bug tracking systems is its status. The status records the progress of the bug fixing activity, and, as such, provides data to software engineering studies. Figure \ref{fig:bugzilla} shows each status that can be recorded in Bugzilla, along with typical transitions between status values, i.e., the workflow.

@@

In the simplest cases, a bug is created and receive the status \texttt{UNCONFIRMED} (if it was created by a regular user) or \texttt{NEW} (if it was created by a developer). Next, it is ASSIGNED to a developer, and then it is RESOLVED, possibly by fixing it with a patch on the source code. The solution is then VERIFIED by someone in the quality assurance team. If it passes the quality requirements, it is CLOSED when the next release of the software is released. If it does not pass the quality requirements or if the solution only partially fixes the problem, the bug is REOPENED.

In order to understand the bug fixing process of a software team, however, it should be possible to know what activities are performed upon change of status. For example, what steps are made before changing the status of a bug to RESOLVED (fixed)? Has the patch been applied to the version control system or is it presented as diff file attached to the bug report? Has the patched source code been built and made available for end users (e.g., as a nightly build)? The documentation for Bugzilla does not prescribe specific activities for marking a bug as RESOLVED, relegating instead this decision to each software project.

Similarly, what do developers do before marking a bug as VERIFIED? Bugzilla documentation states that, when a bug is VERIFIED, it means that ``QA [quality assurance team] has looked at the bug and the resolution and agrees that the appropriate resolution has been taken''\cite{\url{https://landfill.bugzilla.org/bugzilla-3.6-branch/page.cgi?id=fields.html}}. Again, the definition is loose, although it assumes the existence of a QA role.

The developer documentation for both Eclipse and Netbeans are unclear about how the verification of a bug fix is performed. So, what forms of  software verification are they used in the verification process of these projects?
% In some parts they mention running unit tests, and running a patched version of the software and try to reproduce the bug.

Software verification techniques are classified in static and dynamic [cite Sommervile]. Static techniques include source code inspection, automated static analysis, and formal verification. Dynamic techniques, or testing, involve executing the software system under certain conditions and comparing its actual behavior with the intended behavior. Testing can be done in an improvised way (ad hoc testing), or can be compiled in a list of test cases, which can then be automated (e.g., as unit tests).

While mining bug repositories, one cannot assume that the VERIFIED status comprises all forms of software verification. Also, s/he cannot rely on the information provided by the bug tracking system or the developer documentation for a project, since it can be unspecific. Such information can only be assessed by taking a close look on actual bug reports.
